Template for manuscript

### 2024-12-10 LakeMetabolism_project/Synthesis_21_22_23/report/manuscript.Rnw
Work on manuscript

# packages
require(xtable) # generating latex tables from datasets
require(data.table) # data wrangling
require(readxl) # importing excel tables

@@

\subsection{Data analysis pipeline} \label{subsec:pipeline}

@@

Some of the variables listed above have to be derived from other time series data prior
to estimating lake metabolism,
namely do.sat, k.gas, par, and z.mix.
do.sat was derived by using the function \texttt{o2.at.sat}, which calculates
the equilibrium DO concentration of oxygen in water at supplied conditions.
To estimate k.gas, a gas transfer coefficient model must be fit.
The \texttt{LakeMetabolizer} package offers different methods, and we chose
an empirical wind-based gas exchange model, introduced by Vachon and
Prairie in 2013 \citep{Vachon:2013}. This model not only takes wind into
consideration, but also lake area.
All models of gas exchange 
return a k\textsubscript{600} value, a gas exchange normalized to a Schmidt 
number (Sc) of 600, or O\textsubscript{2} at 17.5 \textdegree{}$C$.
After estimating k\textsubscript{600}, it must be transformed to k.gas by using the
function \texttt{k600.2.kGAS} provided by the \texttt{LakeMetabolizer}
package. par was derived from shortwave irradiation,
which we had available (see section \nameref{subsec:source}).
To achieve this transformation, we used the function \texttt{sw.to.par},
which uses the simple empirical transformation $par = 2.114 \times sw$ \citep{Britton:1976}.
To estimate z.mix, one normally needs a time series profile of water temperature
or water density. Since we did not have such data available, we decided to
simulate actively mixed layer depth by drawing from a uniform distribution
with limits 0 and maximum depth of the lake. The reasoning behind this simulation
is that, although the simulated time series of z.mix likely differing substantially
from the actual, a possible treatment effect of fish versus no fish should still be
consistent, given the simulation is performed equally in all lakes.\smallskip

@@

where $\tau_{w}$ is the precision of the process error.
The important distinction of process and observation error is that
process error affects the state of the system at time
$t + k(k=0, 1, ..., T-t)$, because the state evolves dynamically, whereas
observation error only affects the state of the system at time $t$.

@@

\begin{gather}
x^{2} \label{eq:sys1}\\
x^{3} \label{eq:sys2}
\end{gather}

>>>>

# packages
require(LakeMetabolizer) # Modeling Lake Metabolism
require(dplyr) # data wrangling
require(xtable) # generating latex tables from datasets
require(data.table) # data wrangling
require(readxl) # importing excel tables

@@

\subsection{Data pipeline} \label{subsec:pipeline}

@@

Some of the variables listed above have to be derived from other time series data prior
to estimating lake metabolism,
namely do.sat, k.gas, par, and z.mix.
do.sat was derived by using the function \texttt{o2.at.sat}, which calculates
the equilibrium DO concentration in water at supplied conditions.
To estimate k.gas, a gas transfer coefficient model must be fit.
The \texttt{LakeMetabolizer} package offers different methods, and we chose
an empirical wind-based gas exchange model, introduced by Vachon and
Prairie in 2013 \citep{Vachon:2013}. This model not only takes wind into
consideration, but also lake area. Notably, wind speed has to be normalized
to 10 $m$ sensor height before fitting any gas exchange model, which is achieved
with the function \texttt{wind.scale}.
All models of gas exchange 
return a k\textsubscript{600} value, a gas exchange normalized to a Schmidt 
number (Sc) of 600, or O\textsubscript{2} at 17.5 \textdegree{}$C$.
After estimating k\textsubscript{600}, it must be transformed to k.gas by using the
function \texttt{k600.2.kGAS} provided by the \texttt{LakeMetabolizer}
package. par was derived from shortwave irradiation,
which we had available (see section \nameref{subsec:source}).
To achieve this transformation, we used the function \texttt{sw.to.par},
which uses the simple empirical transformation $par = 2.114 \times sw$ \citep{Britton:1976}.
To estimate z.mix, one normally needs a time series profile of water temperature
or water density. Since we did not have such data available, we decided to
simulate actively mixed layer depth by drawing from a uniform distribution
with limits 0 and maximum depth of the lake. The reasoning behind this simulation
is that, although the simulated time series of z.mix likely differing substantially
from the actual, a possible treatment effect of fish versus no fish should still be
consistent, given the simulation is performed equally in all lakes.\smallskip

@@

where $\tau_{w}$ is the precision of the process error.
The important distinction of process and observation error is that
process error affects the state of the system at time
$t + k (k=0, 1, ..., T-t)$, because the state evolves dynamically, whereas
observation error only affects the state of the system at time $t$.

@@

\begin{gather}
\alpha^{\ast}_{t} =
\begin{cases}
\alpha_{t-1} + \alpha_{t}, & \text{if } k_{t} = 0, \\
\frac{\alpha_{t}}{k_{t-1}} + \frac{-\exp{(-k_{t-1})}\alpha_{t}}{k_{t-1}} +
\exp{(-k_{t-1})}\alpha_{t-1}, & \text{otherwise},
\end{cases} \label{eq:sys1} \\
\alpha_{t} = \mathbf{X}_{t-1}\bm{\beta} + k_{t-1}O_{s,t-1}, \label{eq:sys2} \\
k_{t} = \frac{K^{\ast}_{t}\Delta t}{z_{t}}. \label{eq:sys3}
\end{gather}

In this equation structure, $k_{t}$ is the coefficient of gas exchange;
$\mathbf{X}$ is an $n \times 2$ matrix of predictor variables with $I$
(irradiation in arbitrary light units) in the first column and $\ln{T}$ (\textdegree{}$C$) in the second
column; $\bm{\beta}$ is a $2 \times 1$ vector of parameters to be estimated
($\iota$, $\rho$). $\iota$ represents the parameter for Gross Primary Production
(hereafter GPP), implying a linear relationship between GPP and irradiation, and $\rho$ represents
the parameter for Respiration (hereafter R), implying a log-linear relationship
between R and temperature; $O_{s}$ is the equilibrium DO concentration at
supplied conditions; $K^{\ast}_{t}$ is a stochastic node,
with $K^{\ast}_{t} \sim N(K_{t}, \sigma_{k})$, where $K_{t}$ is the gas exchange
coefficient, and $\sigma_{k}$ the precision thereof; the default precision
is $1/(0.1 \times K_{t})$; finally, $z_{t}$ is the mixed layer depth.

From equation~\ref{eq:sys1}, we can see that if $k_{t} = 0$ (i.e., no gas exchange
with the atmosphere), the oxygen levels in the water are modeled to be additive for each
time step. Furthermore, we can see that the gas exchange coefficient is dependent
on mixed layer depth (equation~\ref{eq:sys3}).

While the estimate of gas exchange coefficient serves as prior information for $K$,
priors for the fitted GPP and R parameters ($\iota$ and $\rho$) can also
be defined. The default priors for $\iota$ and $\rho$ are normal distributions
with mean 0 and variance $1 \times 10^{5}$
($\iota_{t} \sim N(0,10^{5})$, $\rho_{t} \sim N(0,10^{5})$) and were used in our case.

To estimate metabolism, the median of the posterior distribution of the parameters
is used as a scalar estimate. Daily GPP and R estimates represent an integrated
estimate of these scalars over a 24-hour window. Uncertainty of GPP and R
estimates is expressed as the posterior standard deviation of the respective
parameters ($\iota$ and $\rho$), multiplied by the square root of the corresponding
covariate ($I$ and $\ln{T}$). NEP is the sum of GPP and R, and the standard deviation
of NEP is the sum of the standard deviations for GPP and R.

In total, 5 parameters are fit in this Bayesian model, namely $\iota$, $\rho$,
$K$, $\tau_{v}$, and $\tau_{w}$. For all parameters except $K$, (default) minimally
informative priors were used. Regarding $K$, as described above, its estimate
(from the separate gas transfer coefficient model) serves as a prior.

Estimates of the posterior distribution of the parameters were sampled using
Gibbs sampling implemented in Just Another Gibbs Sampler
(\href{https://sourceforge.net/projects/mcmc-jags/files/}{JAGS}). Prior to running
the Bayesian model, it must be installed.

\subsection{Sensitivity analysis for mixed layer depth} \label{subsec:sens}

As mentioned in section~\nameref{subsec:pipeline}, we did not have the necessary
data to estimate mixed layer depth. An initial approach to deal with that problem
was to investigate the effect of different mixed layer depths on the daily metabolism
estimates. For that purpose, we selected a few lakes for different monitoring
periods (2021, 2022, 2023) and assessed the impact of various, constant
mixed layer depths over time on the metabolism results.

<<sensanal, results = "asis", echo=FALSE>>=
# Packages ad functions from Moritz Luehrig's paper
source("../../Literature/Moritz_Luehrig_paper_stuff/methods_packages.R")

# Estimating lake metabolism with free-water oxygen
# See "report_analysis_metabolism_B3P3_2022" for further details
require(LakeMetabolizer)

# For plotting
require(GGally)

# Imputation of NAs for time-series (our NAs are due to outlier processing)
require(imputeTS)

# For Bayesian lake metabolism modeling
require(R2jags) # Also, installing JAGS is necessary under
# http://www.sourceforge.net/projects/mcmc-jags/files

require(ggpubr)
require(grid) # Arranging multiple plots
require(grDevices) # Saving png files

# This is our complete dataset of the sondes measurements 2021
# Measurement Interval: 2 minutes
all <- fread("../../project_21/data/processed_data_sondes/ponds_sonde_data_all.txt")

# Importing the metadata
# Wind and irradiation
# Measurement Interval: 1 hour, hourly averages
# Source: QAS_L automated weather station near Narsarsuaq
# https://dataverse.geus.dk/dataset.xhtml?persistentId=doi:10.22008/FK2/IW73UU
# wind sensor height: 2.65 + 0.4 = ca 3.05m
meta <- fread("../../project_21/data/metadata_metabolism_analysis/metadata_2021.txt")

# Step 1: data formatting ------------------------------------------------------

# Select columns to keep from our time series
all <- all[, c("Pond", "Date_time", "ODO_mgL", "Temp_C")]

# Select Pond B1P1 (Treatment: Fish)
all <- subset(all, Pond == "ERL85")

# Rename
all <- setnames(all,c("Pond", "datetime", "do.obs", "wtr"))

# Isolate the desired period for metabolism estimation
all <- all[c(121:5160),]

# choose desired period for the metadata
meta <- meta[c(1:169),]

# rename
meta <- setnames(meta,c("datetime", "dsr_cor", "wsp"))

meta <- meta %>%
  mutate(datetime = as.POSIXct(format(datetime, format = "%Y-%m-%d %H:01:00", tz = "UTC"), tz = "UTC"))

# Create a new inflated dataset with measurements every 2 minutes
# The hourly mean will be assigned to every observation (2min-interval) within that hour
meta_ext <- meta %>%
  complete(datetime = seq(from = min(datetime), to = max(datetime), by = "2 min"))

# Fill the missing wind speed and irradiation values with the corresponding hourly values using 'fill'
meta_ext <- meta_ext %>%
  fill(wsp, .direction = "up") %>%
  fill(dsr_cor, .direction = "up")

# Shift wind speed and irradiation one row up
meta_ext <- meta_ext %>%
  mutate(wsp = lead(wsp, default = last(wsp))) %>%
  mutate(dsr_cor = lead(dsr_cor, default = last(dsr_cor)))

# Ommit last row (not included in our timeseries)
meta_ext <- meta_ext[-nrow(meta_ext), ]

# Reset row names for the final result
rownames(meta_ext) <- NULL

# Step 2: merge the 2 datasets -------------------------------------------------
all <- merge(meta_ext, all, by = "datetime")

# Step 3: Missing data imputation ----------------------------------------------
# We need a complete ODO_mgL timeseries. Therefore we will impute the missing values
# here, with the package "imputeTS", which is specifically designed to impute time-series
# observations.

colSums(is.na(all))

# Make a timeseries object
ts <- ts(all$do.obs, frequency = 720)

# Impute with imputeTS
imp_all <- na_ma(ts) # use this function!
imp_all <- data.table(imp_all)
imp_all$datetime <- all$datetime

# Check for missing values in the imputed dataset
sum(is.na(imp_all)) # No missing values anymore

# Check imputation by plotting the original and the imputed dataset
plot(x = all$datetime, y = all$do.obs, type = "l", col = "blue", lwd = 2)
lines(x = imp_all$datetime, y = imp_all$imp_all, type = "l",
      col = rgb(1, 0, 0, alpha = 0.3), lwd = 2)
# The imputation worked very well!

# Replace original column with imputed column
all$do.obs <- imp_all$imp_all
sum(is.na(all))

# Step 4: Model choice ---------------------------------------------------------
# Gas transfer coefficient model: kvachon()
# - needs wind speed, sensor height, and lake area

# Lake metabolism model: metab.bayesian()
# Most flexible model

# Step 5: Calculate k600 using the Cole method ---------------------------------

# This function needs specific column names
all$wnd <- all$wsp
all$wsp <- NULL

# Normalize wind to 10m sensor height
wind.scale <- wind.scale(all, wnd.z = 3.05)

all <- merge(all, wind.scale, by = "datetime")

all$wnd <- all$wnd_10
all$wnd_10 <- NULL

# Also only the 2 columns of interest, otherwise it gets confused
all.600 <- all[,c("datetime","wnd")]
k600.vachon <- k.vachon(all.600, lake.area = 18200)

# Merge
all <- merge(all, k600.vachon, by = "datetime")

# Step 6: Calculate gas-specific k600 ------------------------------------------

kgas <- k600.2.kGAS(all)

# Merge
all <- merge(all, kgas, by = "datetime")

# only keep k.gas
all$k600 <- NULL

# Step 7: Calculate dissolved oxygen saturated (do.sat) ------------------------

# I know that the sonde has do.sat measurements, but I have more faith
# in the authors of this paper to calculate a more accurate do.sat then the
# sonde-intern calculations.

o2.sat <- o2.at.sat(all[,c('datetime','wtr')])

# Merge
all <- merge(all, o2.sat, by = "datetime")

# Step 8: Derive photosynthetically active radiation (par) from shortwave irradiation (sw) ----
# Here, I take the downwelling shortwave irradiation (tilt corrected) from the
# QAS_L automated weather station a couple of kilometers away from Narsarsuaq
# It's the closest weather station measuring this parameter, that I could find.

# Derive par from sw
par <- sw.to.par(all, sw.col = "dsr_cor")
rownames(par) <- NULL

# Merge
all <- merge(all, par[,c("datetime", "par")], by = "datetime")

# Step 9: Calculate Actively mixed layer depth (z.mix) -------------------------

################################################################################
# Set different mixed layer depths of sensitivity analysis
# For some reason, metab.bayesian does not recognize z.mix columns
# if they are not named "z.mix", hence I have to create a dataset for each z.mix
################################################################################

all2 <- all
all2$z.mix <- 0.5

all3 <-all
all3$z.mix <- 1

all4 <- all
all4$z.mix <- 2

all5 <- all
all5$z.mix <- 3

all6 <- all
all6$z.mix <- 4

all7 <- all
all7$z.mix <- 5

all8 <- all
all8$z.mix <- 6

all9 <- all
all9$z.mix <- 7

# Step 10: Fit model -----------------------------------------------------------

# Choose columns to keep
all2 <- all2[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
all3 <- all3[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
all4 <- all4[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
all5 <- all5[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
all6 <- all6[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
all7 <- all7[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
all8 <- all8[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]
all9 <- all9[,c("datetime", "do.obs", "do.sat", "k.gas", "z.mix", "par", "wtr")]

# Mixed layer depth 0.5m over the whole observation period
bayesian.res_0.5 <- metab(all2, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                          irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                          do.sat.name = "do.sat")

# Mixed layer depth 1m over the whole observation period
bayesian.res_1 <- metab(all3, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                        do.sat.name = "do.sat")

# Mixed layer depth 2m over the whole observation period
bayesian.res_2 <- metab(all4, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                        do.sat.name = "do.sat")

# Mixed layer depth 3m over the whole observation period
bayesian.res_3 <- metab(all5, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                        do.sat.name = "do.sat")

# Mixed layer depth 0.5m over the whole observation period
bayesian.res_4 <- metab(all6, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                          irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                          do.sat.name = "do.sat")

# Mixed layer depth 1m over the whole observation period
bayesian.res_5 <- metab(all7, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                        do.sat.name = "do.sat")

# Mixed layer depth 2m over the whole observation period
bayesian.res_6 <- metab(all8, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                        do.sat.name = "do.sat")

# Mixed layer depth 3m over the whole observation period
bayesian.res_7 <- metab(all9, method="bayesian", wtr.name='wtr', do.obs.name='do.obs',
                        irr.name='par', z.mix = "z.mix", k.gas.name = "k.gas",
                        do.sat.name = "do.sat")

# Get standard deviations of estimates
bayesian.sd_0.5 <- attr(bayesian.res_0.5, "metab.sd")
bayesian.sd_1 <- attr(bayesian.res_1, "metab.sd")
bayesian.sd_2 <- attr(bayesian.res_2, "metab.sd")
bayesian.sd_3 <- attr(bayesian.res_3, "metab.sd")
bayesian.sd_4 <- attr(bayesian.res_4, "metab.sd")
bayesian.sd_5 <- attr(bayesian.res_5, "metab.sd")
bayesian.sd_6 <- attr(bayesian.res_6, "metab.sd")
bayesian.sd_7 <- attr(bayesian.res_7, "metab.sd")

# Create a date variable
bayesian.res_0.5$Date <- as.Date(paste(bayesian.res_0.5$year, "-", bayesian.res_0.5$doy, sep = ""), format = "%Y-%j")
bayesian.res_1$Date <- as.Date(paste(bayesian.res_1$year, "-", bayesian.res_1$doy, sep = ""), format = "%Y-%j")
bayesian.res_2$Date <- as.Date(paste(bayesian.res_2$year, "-", bayesian.res_2$doy, sep = ""), format = "%Y-%j")
bayesian.res_3$Date <- as.Date(paste(bayesian.res_3$year, "-", bayesian.res_3$doy, sep = ""), format = "%Y-%j")
bayesian.res_4$Date <- as.Date(paste(bayesian.res_4$year, "-", bayesian.res_4$doy, sep = ""), format = "%Y-%j")
bayesian.res_5$Date <- as.Date(paste(bayesian.res_5$year, "-", bayesian.res_5$doy, sep = ""), format = "%Y-%j")
bayesian.res_6$Date <- as.Date(paste(bayesian.res_6$year, "-", bayesian.res_6$doy, sep = ""), format = "%Y-%j")
bayesian.res_7$Date <- as.Date(paste(bayesian.res_7$year, "-", bayesian.res_7$doy, sep = ""), format = "%Y-%j")

# Select columns to keep
bayesian.res_0.5 <- bayesian.res_0.5[,c("Date", "GPP", "R", "NEP")]
bayesian.res_1 <- bayesian.res_1[,c("Date", "GPP", "R", "NEP")]
bayesian.res_2 <- bayesian.res_2[,c("Date", "GPP", "R", "NEP")]
bayesian.res_3 <- bayesian.res_3[,c("Date", "GPP", "R", "NEP")]
bayesian.res_4 <- bayesian.res_4[,c("Date", "GPP", "R", "NEP")]
bayesian.res_5 <- bayesian.res_5[,c("Date", "GPP", "R", "NEP")]
bayesian.res_6 <- bayesian.res_6[,c("Date", "GPP", "R", "NEP")]
bayesian.res_7 <- bayesian.res_7[,c("Date", "GPP", "R", "NEP")]

# Create a date variable
bayesian.sd_0.5$Date <- as.Date(paste(bayesian.sd_0.5$year, "-", bayesian.sd_0.5$doy, sep = ""), format = "%Y-%j")
bayesian.sd_1$Date <- as.Date(paste(bayesian.sd_1$year, "-", bayesian.sd_1$doy, sep = ""), format = "%Y-%j")
bayesian.sd_2$Date <- as.Date(paste(bayesian.sd_2$year, "-", bayesian.sd_2$doy, sep = ""), format = "%Y-%j")
bayesian.sd_3$Date <- as.Date(paste(bayesian.sd_3$year, "-", bayesian.sd_3$doy, sep = ""), format = "%Y-%j")
bayesian.sd_4$Date <- as.Date(paste(bayesian.sd_4$year, "-", bayesian.sd_4$doy, sep = ""), format = "%Y-%j")
bayesian.sd_5$Date <- as.Date(paste(bayesian.sd_5$year, "-", bayesian.sd_5$doy, sep = ""), format = "%Y-%j")
bayesian.sd_6$Date <- as.Date(paste(bayesian.sd_6$year, "-", bayesian.sd_6$doy, sep = ""), format = "%Y-%j")
bayesian.sd_7$Date <- as.Date(paste(bayesian.sd_7$year, "-", bayesian.sd_7$doy, sep = ""), format = "%Y-%j")

# Select columns to keep
bayesian.sd_0.5 <- bayesian.sd_0.5[,c("Date", "GPPsd", "Rsd", "NEPsd")]
bayesian.sd_1 <- bayesian.sd_1[,c("Date", "GPPsd", "Rsd", "NEPsd")]
bayesian.sd_2 <- bayesian.sd_2[,c("Date", "GPPsd", "Rsd", "NEPsd")]
bayesian.sd_3 <- bayesian.sd_3[,c("Date", "GPPsd", "Rsd", "NEPsd")]
bayesian.sd_4 <- bayesian.sd_4[,c("Date", "GPPsd", "Rsd", "NEPsd")]
bayesian.sd_5 <- bayesian.sd_5[,c("Date", "GPPsd", "Rsd", "NEPsd")]
bayesian.sd_6 <- bayesian.sd_6[,c("Date", "GPPsd", "Rsd", "NEPsd")]
bayesian.sd_7 <- bayesian.sd_7[,c("Date", "GPPsd", "Rsd", "NEPsd")]

# Merge
bayesian.merge_0.5 <- merge(bayesian.res_0.5, bayesian.sd_0.5, by = "Date")
bayesian.merge_1 <- merge(bayesian.res_1, bayesian.sd_1, by = "Date")
bayesian.merge_2 <- merge(bayesian.res_2, bayesian.sd_2, by = "Date")
bayesian.merge_3 <- merge(bayesian.res_3, bayesian.sd_3, by = "Date")
bayesian.merge_4 <- merge(bayesian.res_4, bayesian.sd_4, by = "Date")
bayesian.merge_5 <- merge(bayesian.res_5, bayesian.sd_5, by = "Date")
bayesian.merge_6 <- merge(bayesian.res_6, bayesian.sd_6, by = "Date")
bayesian.merge_7 <- merge(bayesian.res_7, bayesian.sd_7, by = "Date")

# create Z.mix variable identifier
bayesian.merge_0.5$z.mix <- "0.5m"
bayesian.merge_1$z.mix <- "1m"
bayesian.merge_2$z.mix <- "2m"
bayesian.merge_3$z.mix <- "3m"
bayesian.merge_4$z.mix <- "4m"
bayesian.merge_5$z.mix <- "5m"
bayesian.merge_6$z.mix <- "6m"
bayesian.merge_7$z.mix <- "7m"

# Merge
bayesian.merge.all <- rbind(bayesian.merge_0.5, bayesian.merge_1,
                            bayesian.merge_2, bayesian.merge_3, bayesian.merge_4,
                            bayesian.merge_5, bayesian.merge_6, bayesian.merge_7)

# Step 11: Visualize the results -----------------------------------------------

# GPP
p1 = ggplot(data = bayesian.merge.all, aes(x=Date, y=GPP, color=z.mix)) + theme_light() +
  geom_line(data = subset(bayesian.merge.all, z.mix == "0.5m")) +
  geom_errorbar(aes(ymin = GPP-GPPsd, ymax = GPP+GPPsd), width = 0.12) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "1m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "2m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "3m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "4m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "5m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "6m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "7m")) +
  ylab(expression(paste("GPP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))

# R
p2 = ggplot(data = bayesian.merge.all, aes(x=Date, y=R, color=z.mix)) + theme_light() +
  geom_line(data = subset(bayesian.merge.all, z.mix == "0.5m")) +
  geom_errorbar(aes(ymin = R-Rsd, ymax = R+Rsd), width = 0.12) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "1m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "2m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "3m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "4m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "5m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "6m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "7m"))
  ylab(expression(paste("R (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))

# NEP
p3 = ggplot(data = bayesian.merge.all, aes(x=Date, y=NEP, color=z.mix)) + theme_light() +
  geom_line(data = subset(bayesian.merge.all, z.mix == "0.5m")) +
  geom_errorbar(aes(ymin = NEP-NEPsd, ymax = NEP+NEPsd), width = 0.12) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "1m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "2m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "3m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "4m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "5m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "6m")) +
  geom_line(data = subset(bayesian.merge.all, z.mix == "7m"))
  ylab(expression(paste("NEP (", O[2], " in mg L", NULL^-1, " day", NULL^-1, ")")))

# Plots of ecosystem parameters
p4 = ggplot((all)) + theme_light() +
  geom_line(aes(y=do.obs, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("DO (mg L",NULL^-1,")")))

p5 = ggplot((all)) + theme_light() +
  geom_line(aes(y=do.sat, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("Equilibrium\nDO concentration (mg L",NULL^-1,")")))

p6 = ggplot((all)) + theme_light() +
  geom_line(aes(y=wtr, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab("Temperature in °C")

p7 = ggplot((all)) + theme_light() +
  geom_line(aes(y=par, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("PAR (",mu,"mol m",NULL^-2," s",NULL^-1,")")))

p8 = ggplot((all)) + theme_light() +
  geom_line(aes(y=k.gas, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab(expression(paste("Gas and temperature specific\ngas transfer coefficient (m",NULL^-1,")")))

p9 = ggplot((all)) + theme_light() +
  geom_line(aes(y=wnd, x=datetime), color = "gray17") +
  rremove("xlab") +
  ylab("Wind speed (m/s)")

fig2 <- ggarrange(p1 + rremove("xlab"), p2 + rremove("xlab"), p3 + rremove("xlab"),
                  p4 + rremove("xlab"), p5 + rremove("xlab"), p6 + rremove("xlab"),
                  p7 + rremove("xlab"), p8 + rremove("xlab"), p9 + rremove("xlab"),
                  nrow=5, ncol = 2,  common.legend = TRUE, legend = "right")

annotate_figure(fig2)
@
